Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-12-15 cogsci/cogsci.tex
sim exp

---
title: "Word Learning as Network Growth: A Cross-linguistic Analysis"

bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

header-includes:
   - \usepackage[subtle]{savetrees}

author-information: > 
    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract:

    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."

keywords:
    "semantic network, phonological network, network growth, mechanism of word learning"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())

#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
#                      echo=F, warning=F, cache=F, message=F, sanitize = T)

knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)

```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
```

# Introduction

How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998). Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.

We know that similarity affect word recognition in both adults and children. For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).

Crucially, similarity influences not only the recognition of know words, but also the learning of novel words. In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew). When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din"). In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).

That said, previous experimental work has studied the effect of phonological and semantic similarity separately. Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).  However, children  acquire a lexicon which is more richly structured than these special cases. In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains. Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.

One could imagine two learning scenarios. On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al. 1975). For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity. Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms. On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002). Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension. In this study, we explore these hypothesis, bla bla

A second goal of this work is to investigate how the learning mechanism develops over the life span. According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors. To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.  A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind. For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al. 2013; Pajak et al. 2016). Here we explore

@@

# Experiment 1
Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.

## Methods

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as specified in the pre-registration).

### Stimuli
The sound stimuli were generated using the MBROLA Speech Synthesizer (Cite) using an American English voice. We generated two similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof"). We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
As for the objects used as semantic referents, we used the Dynamic Categories Stimuli (Cite) which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish" (plus the additional category "flower" for the catch trial). These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated instances that varied in their similarity by manipuating a continuous property controling features of the category's shape. This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower". All these continous properties varied on a scale from 0 to 1. We generated "similar" and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively. Examples of the resuting pairs are shown in Figure XX.

###Design 
The experiment consisted of 4 conditions which consisted, each, of a pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar to the previous ones. It involved different sounds and different objects, and it was used only to select participant who were able to follow the instructions and show minimal learning (not at chance level).

### Procedure
Children were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.

@@

The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial. The experiment can be views online using this link XX.

### Results

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first."}

img <- png::readPNG("figs/growth2.png")
grid::grid.raster(img)

```

Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process. Third, it tests the generality of the findings across eight languages.

```{r }

#Import data from saved
data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")

#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long <- data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))

data_long$predictor <- mapValues(data_long$predictor, 
                                 from = c("PAC_assoc", "PAC_phono_t2"), 
                                 to = c("Sem.", "Phono."))

#Compute the correlations 
correlations <-  data_long %>%
  group_by(language, predictor) %>%
  dplyr::summarise(cor = round(cor(AoA, value), 2))

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_data_all
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```

```{r }

#Import data from saved
degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
  dplyr::rename(Dimension = dimension)

plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
  facet_grid(. ~ language)+
  geom_point(size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme_few()+
  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
  xlab("degree") +ylab("probability")

ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)

```

```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph."}
plot_dist
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```

# Networks
## Data
We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months). Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns. We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \ref{tab:stats} gives an overview of the data used. Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available. Note, however, that all languages have at least 60% of nouns translated.

```{r stats, results="asis", echo=FALSE}

statistics <- feather::read_feather("../saved_data/statistics.feather") 
rownames(statistics) <- NULL

tab <- xtable::xtable(statistics,
                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")

print(tab, type="latex", comment = F, table.placement = "H")

#print(statistics, type="latex", comment = F, table.placement = "H")
```

## Semantic networks

We constructed semantic networks following the procedure outlined in @hills2009. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

## Phonological networks

We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1. When using this threshold, the resulting networks were too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2. The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

<!--## Network growth

We tested two network growth scenarios discussed in @hills2009. The first one was *Preferential Attachment* (PAT). According to this mechanism, the network structure of known words predicts what words will be learned next. A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network. The second mechanism was *Preferential Acquisition* (PAC). In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.  Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network. For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to. Thus, according to PAT, the node N1 is more likely to enter the lexicon first. For PAC, each candidate node was characterized with its degree in the entire network. According th PAC, the node N3 is more likely to enter the lexicon first.

-->

# Analysis

## Static properties of the global network

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months). This global network is the end-state towards which both PAT and PAC should converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that are relevant to PAC and/or PAT.

###Connectivity predicts the age of acquisition

@@

We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g. "father" counts as "daddy"). For word length, we counted the number of phonemes in our generated IPA transcription.

>>>>

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{Word Learning as Network Growth: A Cross-linguistic Analysis}

\usepackage[subtle]{savetrees}

\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

\begin{document}

\maketitle

\begin{abstract}
Children tend to produce words earlier when they are connected to a
variety of other words along both the phonological and semantic
dimensions. Though this connectivity effect has been extensively
documented, little is known about the underlying developmental
mechanism. One view suggests that learning is primarily driven by a
network growth model where highly connected words in the child's early
lexicon attract similar words. Another view suggests that learning is
driven by highly connected words in the external learning environment
instead of highly connected words in the early internal lexicon. The
present study tests both scenarios systematically in both the
phonological and semantic domains, and across 8 languages. We show that
external connectivity in the learning environment drives growth in both
the semantic and the phonological networks, and that this pattern is
consistent cross-linguistically. The findings suggest a word learning
mechanism where children harness their statistical learning abilities to
(indirectly) detect and learn highly connected words in the learning
environment.

\textbf{Keywords:}
semantic network, phonological network, network growth, mechanism of
word learning
\end{abstract}

\section{Introduction}\label{introduction}

How do children acquire words? An important step consists in mapping a
phonological form (e.g.~the sound ``cat'') to a semantic referent (the
concept CAT). A large body of work has been devoted to explore the
mechanism of this mapping (Quine, 1960; Markman, 1990; Smith and Yu,
2008). However, words do not exist in a vacuum; they are organized into
a strcuture based on both semantic and phonological similarity
principles (e.g., Collins \& Loftus, 1975; Luce \& Pisoni, 1998). A more
accurate understanding of word learning should account not only for how
sounds are mapped to meanings, but also for how sound similarity and
meaning similarity may influence the process of aqusition.

We know that similarity affect word recognition in both adults and
children. For example, exposure to a word such as ``cat'' influences
subsequent recognition of phonologically and smantically similar words
like ``cab'' and ``dog'' (Goldinger, Luce \& Pisoni, 1989; McNamara,
2006; Arias-Trejo \& Plunkett, 2010; Mani \& Plunkett, 2011).

Crucially, similarity influences not only the recognition of know words,
but also the learning of novel words. For example, Swingley \& Aslin
(2007) showed that infants found it more challenging to learn the
meaning of a novel word such as ``tog'' (which is similar a the familiar
word ``dog'') than to learn the meaning of a word such as ``shang''
(which is not similar to any words children knew). When learning two
novel words, Stager and Werker (1997) found that infatns were more
likely to succeed when these words were phonologically distant (e.g.,
``lif''/``neem''), than when they were phonologcially simialr
(``bin/''din``). Besides, children learn the semantic relationship among
newly learned words spontaneousely (Wojcik \& Saffran, 2013), and they
prioritize the acquisition of words that are distinct in the semantic
space (Engelthaler \& Hills, 2017).

That said, previous experimental work has studied the effect of
phonological and semantic similarity separately. Some studied the
mechanism of word learning using a toy lexicon where only the
phonological similarity varied (e.g., Stager and Werker, 1997), and
others studied the learning of a toy lexicon where only the semantic
similarity varied (e.g., Wojcik \& Saffran, 2013). However, children
acquire a lexicon which is more richly structured than these special
cases. In particular, as reviewed abvove, the end-state lexicon involves
variability along both the phonological and semantic domains. Thus, to
have a deeper understanding of word acquisition in the real world, it is
crucial to study how learners acquire a lexicon that simulates this
bi-dimensional variation.

One could imagine two learning scenarios. On the first one, children's
learning, at least in some challenging situations, is primarily
determined by one dimension (Sloutsky \& Napolitano, 2003; Colavita et
al. 1975). For example, it is possible that similar sounding words are
confusable and hard to learn regardless of their semantic similarity.
Vice-versa, similar meanings might be challenging to learn regardless of
the phonological similarity of their forms. On the second scenario,
learners combine cues from both dimensions to optimize their learning
(Fourtassi and Frank, 2018; Ernst \& Banks, 2002). Thus, confusability
that may arise from high similarity along one dimension can be mitigated
via higher distance from the other dimension. In this study, we explore
these hypothesis, bla bla

A second goal of this work is to investigate how the learning mechanism
develops over the life span. According to one hypothesis, adults use
qualitatively distinct learning mechanisms than children, due, for
example, to maturational factors. To illustrate, in the experimental
setting used in Stager and Werker (1997), children's difficulty with
learning similar sounding words--despite their ability to perceptually
differentiate them--might be attributed to their inferior working
memory, hindering their ability to attend simultaneously to the sound
contrast and the meanings. A second hypothesis proposes that learners
use fundamentally similar mechanisms across the life span, and that the
difference might be one of degree, not kind. For example, though they
have vastly greater working memory capacity, adults show patterns of
word processing and learning which parallel results obtained with
children in Stager and Werker's study (White et al. 2013; Pajak et al.
2016). Here we explore

@@

\section{Experiment 1}\label{experiment-1}

Children were trained to learn the association between pairs of
nonesense words (e.g., ``lif''/``neem'') and pairs of objects (e.g., two
flowers). After training, children performed a series of two-alternative
forced choices. In each testing trial, one of the two sounds is uttered
(e.g., ``lif'') and participants choose the corresponding object from
the two alternatives (e.g., flower 1 or flower 2). Each child learned an
artificial lexicon where both the pairs of sounds and the pairs of
objects can be similar or different. Our predictions were as follows. If
the sound and meaning interact in word learning, then the pair of words
that differ on both the meaning and sound levels should be the easiest
to learn, followed by the pairs of words that are different on one
level, but similar on another level. Finally, the pair of words that are
similar on both levels should be the most difficult to learn.

\subsection{Methods}\label{methods}

\subsubsection{Participants}\label{participants}

We planned to recruit a sample of 60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. So far, we
collected data from N=47 children (mean age= months, F=). An additional
28 children participated but were removed from analyses because they
were not above chance on the catch trials (as specified in the
pre-registration).

\subsubsection{Stimuli}\label{stimuli}

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Cite) using an American English voice. We generated two similar sound
pairs (``aka''/``ama'' and ``ada''/``aba'') and two different sound
pairs (``lif''/``neem'' and ``zem''/``doof''). We generated a addtional
pair (``nak''/``veep'') which we used in the catch trial (see
Procedure). As for the objects used as semantic referents, we used the
Dynamic Categories Stimuli (Cite) which allowed us to generate objects
in four different categories: ``tree'', ``bird'', ``bug'', and ``fish''
(plus the additional category ``flower'' for the catch trial). These
categories are supposed to be naturally occuring kinds that might be
seen on an alien planet. In each category, we generated instances that
varied in their similarity by manipuating a continuous property
controling features of the category's shape. This property was the head
fatness for the category ``bug'', the body strech for ``bird'', the tail
size relative to the body fatness for ``fish'', the width of the trunk
for ``tree'', and finally center size for ``flower''. All these
continous properties varied on a scale from 0 to 1. We generated
``similar'' and ``different'' objects' pairs (whithin each category) by
setting the values of this properties to 0 and 0.5, and to 0 and 1,
respectively. Examples of the resuting pairs are shown in Figure XX.

\subsubsection{Design}\label{design}

The experiment consisted of 4 conditions which consisted, each, of a
pair of sounds-objects associations. These conditions were constructed
by crossing the sound's degree of similarity with the object's degree of
similarity leading to a 2x2 factorial design. Besides the 4 conditions,
we also tested participants on a fifth catch condition which was similar
to the previous ones. It involved different sounds and different
objects, and it was used only to select participant who were able to
follow the instructions and show minimal learning (not at chance level).

\subsubsection{Procedure}\label{procedure}

Children were asked if they would be willing to play a game on a tablet
with the experimenter and were informed that they could stop playing at
any time. The experimenter explained that the game consisted in learning
some words spoken in an alien planet. The experiment began with two
simple examples (not included in the analysis), and in these examples
children were given feedback from the experimenter so as to make sure
they correctly understood the structure of the task. After the
introduction and examples, children were tested in a sequence of five
conditions: the four experimental conditions plus the catch condition.
In each condition, participants saw a first block of four exposure
trials followed by four testing trials, and a second block of two
exposure trials (for memory refreshment) follwoed by an additional four
testing trials.

@@

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial. The experiment can be views online using this link XX.

\subsubsection{Results}\label{results}

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/growth-1}

}

\caption{\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}
\end{CodeChunk}

Studies that investigate lexical network growth have focused on semantic
networks using English data (Hills, Maouene, Riordan, \& Smith, 2010;
Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Steyvers \& Tenenbaum,
2005). The novelty of the current study is threefold: First, it
investigates whether phonological networks, like semantic networks, grow
by PAC, or if they rather grow by PAT. Second, it provides a systematic
comparison of both network growth scenarios in the phonological and the
semantic domains and assesses their relative contribution to the
learning process. Third, it tests the generality of the findings across
eight languages.

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/all_data-1}

}

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/degree_distribution-1}

}

\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
\end{figure*}
\end{CodeChunk}

\section{Networks}\label{networks}

\subsection{Data}\label{data}

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). We used the
\emph{Words and Sentences} version of the CDI which contains the
productive vocabulary of toddlers (age varied between 16 to 36 months).
Following previous studies (Hills et al., 2009; Storkel, 2009), we
restricted our analysis to nouns. We defined the age of acquisition of a
given word by the month at which this word was produced by at least 50\%
of children (J. C. Goodman, Dale, \& Li, 2008), and we excluded nouns
that have not been learned (according to this criterion) by the last
month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English,
Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
nouns that had entries in the Florida Association Norms (see below).
Since these norms are available only in English, we used the
hand-checked translation equivalents provided by Braginsky, Yurovsky,
Marchman, \& Frank (2016), allowing us to use the English association
norms across languages. Table \ref{tab:stats} gives an overview of the
data used. Translation equivalents were originally constructed for a
subset of words appearing on the toddler CDI form, and so not all words
are currently available. Note, however, that all languages have at least
60\% of nouns translated.

\begin{table}[H]
\centering
\begin{tabular}{rlrrr}
  \hline
 & language & total & translated & normed \\ 
  \hline
1 & Croatian & 253 & 177 & 170 \\ 
  2 & Danish & 295 & 198 & 187 \\ 
  3 & English & 296 & 296 & 274 \\ 
  4 & Italian & 311 & 203 & 194 \\ 
  5 & Norwegian & 305 & 193 & 186 \\ 
  6 & Russian & 311 & 311 & 285 \\ 
  7 & Spanish & 240 & 173 & 163 \\ 
  8 & Turkish & 293 & 175 & 164 \\ 
   \hline
\end{tabular}
\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).} 
\end{table}

\subsection{Semantic networks}\label{semantic-networks}

We constructed semantic networks following the procedure outlined in
Hills et al. (2009). We used as an index of semantic relatedness the
Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
This dataset was collected by giving adult participants a word (the
cue), and asking them to write the first word that comes to mind (the
target). For example, when given the word ``ball'', they might answer
with the word ``game''. A pair of nodes were connected by a directed
link from the cue to the target if there was a cue-target relationship
between these nodes in the association norms. The connectivity of a
given node was characterized by its \emph{indegree}: the number of links
for which the word was the target. To model growth from month to month,
we constructed a different network at each month, based on the words
that have been acquired by that month.

\subsection{Phonological networks}\label{phonological-networks}

We generated approximate International Phonetic Alphabet (IPA)
transcriptions from the orthographic transcription, across languages,
using the open source text-to-speech software
\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
the Levenshtein distance (also known as edit distance) as a measure of
phonological relatedness between two nodes. The measure counts the
minimum number of operations (insertions, deletions, substitutions)
required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (e.g., Storkel, 2009). However, in these previous studies the
network was built using an adult vocabulary. In the current study,
however, network growth models are based on the children's early
vocabulary which contains very few word pairs with an edit distance of
1. When using this threshold, the resulting networks were too sparse and
uninformative. Thus, we increased the threshold from 1 to 2, that is,
two nodes were related if their edit distance was equal to 1 or 2. The
connectivity of a given node was characterized with its \emph{degree}:
the number of links it shares with other words.

\section{Analysis}\label{analysis}

\subsection{Static properties of the global
network}\label{static-properties-of-the-global-network}

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds to the network
by 30 months). This global network is the end-state towards which both
PAT and PAC should converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that are relevant to PAC
and/or PAT.

\subsubsection{Connectivity predicts the age of
acquisition}\label{connectivity-predicts-the-age-of-acquisition}

@@

We used the frequency estimates from Braginsky et al. (2016) where
unigram counts were derived based on CHILDES corpora in each
language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
For each word, counts included words that shared the same stem (e.g.,
``cats'' counts as ``cat''), or words that were synonymous (e.g.
``father'' counts as ``daddy''). For word length, we counted the number
of phonemes in our generated IPA transcription.
